---
output: html_document
params: 
  species: NA
  ct_dat : NA
  individuals : NA
  place: NA
  year: NA
---

---
title: "<center>PAWS Report `r params$place` `r params$year`"
date: "<center>March 19, 2019"
---
<center>

##Species Detection Maps

##### Interactive Maps of the same can be viewed in this link:

```{r test, echo = F, warning = F}
# The `params` object is available in the document.
detectionMaps(CTtable = params$ct_dat, recordTable = params$species, Xcol = "utm_x", Ycol = "utm_y", stationCol = "Station",
              speciesCol = "Species", richnessPlot = TRUE, speciesPlots = TRUE, addLegend = TRUE,  printLabels = FALSE,
              writePNG = F, plotR=T, plotDirectory = FALSE)
```


*****

##Species Time Activity

```{r timeActivity, echo = F}
activityHistogram(recordTable=params$species, 
                  allSpecies = TRUE, 
                  speciesCol = "Species", 
                  recordDateTimeCol = "DateTimeOriginal", 
                  recordDateTimeFormat = "%Y-%m-%d %H:%M:%S")

```


******

##SECR
</center>

#####The SECR estimate has been run on a naive **null model** with starting parameters as: D =.00002, g0 = 0.02, sigma = 25000.

#####These results have been provided for error checking purposes. **The estimates should be interpreted and shared with caution**. 

```{r secr, echo = F}
CamMatrix<-cameraOperation(CTtable = params$ct_dat, stationCol = "Station", setupCol = "Setup_date", retrievalCol = "Retrieval_date", 
                           byCamera = FALSE, allCamsOn = TRUE, dateFormat = "%Y-%m-%d", hasProblems = F, writecsv = FALSE, 
                           outDir = getwd())

input_secr <- spatialDetectionHistory(recordTableIndividual =  params$individuals, species = "Snow leopard", camOp = CamMatrix, CTtable = params$ct_dat, output = "binary",
                                    stationCol = "Station", speciesCol = "Species", Xcol = "utm_x", Ycol = "utm_y", individualCol = "Individual", 
                                    recordDateTimeCol = "DateTimeOriginal", recordDateTimeFormat = "%Y-%m-%d %H:%M:%S", occasionLength = 1, occasionStartTime = 12, 
                                    day1 = "survey", includeEffort = TRUE, binaryEffort = TRUE, timeZone = "Asia/Bishkek")

mask <- make.mask(traps(input_secr), buffer = 28000, type = 'trapbuffer')
fit<-secr.fit(input_secr, mask = mask, model = g0~1, start = list(D=.00002, g0= 0.02, sigma= 25000), trace = FALSE)
#esa.plot(fit, ylim=c(0,0.006), xlim=c(0,4000))
predict(fit)

fit

summary(input_secr, terse = TRUE)


```